### 2017-02-27 readme.Rmd
update readme

Let's compare to a PA sdm - hopefully we are in the right ball park
```{r,message=FALSE,error=FALSE,warning=FALSE}
d <- sdmData(formula= ~., train=species, predictors=preds)
m1 <- sdm(Occurrence~.,data=d,methods=c('gam'))
p1 <- predict(m1,newdata=preds)
plot(p1)
```
### References 
Grafström, Anton, and Yves Tillé. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.

>>>>

Let's compare to a PA sdm - hopefully we are in the right ball park
```{r,message=FALSE,error=FALSE,warning=FALSE}
d <- sdmData(formula= ~., train=species, predictors=preds)
dat <- cbind(species$Occurrence,d@features)
colnames(dat)[1]<-'occurrence'
fm2 <- gam(occurrence ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation),
              data = dat,
              family = binomial())

p2 <- predict(object=preds,
             model=fm2,
             type = 'response')
plot(p2)
```
### References 
Grafström, Anton, and Yves Tillé. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.
